% dwarak.tex
% Template by Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 



\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}   
\usepackage[pdftex]{hyperref}
\usepackage{ragged2e}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black 
    %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://dwarak.in/}{\LARGE Dwaraka Nath}} & \href{mailto:dtsdwarak@gmail.com}{dtsdwarak@gmail.com}\\
	{\footnotesize \texttt{\#17/66, 2nd Avenue, Prithivipakkam, Ambattur, Chennai.}} & \href{https://dwarak.in}{https://dwarak.in} \\
	\end{tabular*}
\\
\vspace{0.3in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{About self}
    \begin{flushleft}
    \justifying
    \small  {
    I have over four years of experience working in the technology industry building products and services across a spectrum of client portfolios. In that capacity, I had the opportunity to take up diverse roles - from a software engineer in the corporate building tech based solutions, to being an editor for an online magazine, to training fellows in a networking institute, leading a community initiative to create and manage content, build strategy, oversee liaison efforts with print magazines for Mozilla Foundation and writing code for projects in the open source domain as an individual contributor. And very recently, I have also started working as a digital literacy consultant for curriculum and content management for kids, learning under the aegis of TeachForIndia Foundation.}
    \end{flushleft}
    
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Personal Information}
	\begin{description}
		\item[Languages:] { \footnotesize English, Tamil, Telugu, Hindi
		}
		\item[Nationality] { \footnotesize India
		}
	\end{description} % End Skills list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{{Birla Institute of Technology and Science}}{Pilani, India}{{Master of Engineering in Software Systems};{ CGPA:8.81}}{July 2014 -- June 2016}
		\item
			\ressubheading{{SSN College of Engineering}}{Chennai, India}{{Bachelor of Engineering in ECE};{ CGPA:7.59}}{August 2009 -- May 2013}
		\item
			\ressubheading{{DAV Boys Senior Secondary School}}{Chennai, India}{{AISSE};{ Percentage:94.2}}{May 2009}			
	\end{itemize} % End Education list


%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{itemize}
	    \item 
			\ressubheading{\href{http://www.amazon.in/}{Amazon}}{Bangalore, India}
				{Software Development Engineer}{June 2016 -- Present}
				{ \footnotesize
				\begin{itemize}
					\resitem{Working on Amazon.in  - Seller Experience Platform}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.orangescape.com/}{OrangeScape}}{Chennai, India}
				{Software Engineering Intern}{May 2015 -- July 2015}
				{ \footnotesize
				\begin{itemize}
					\resitem{Developed a module to crowdsource language translations from users}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.listertechnologies.com/}{Lister Technologies}}{Chennai, India}
				{Software Engineer}{July 2013 -- July 2014}
				{ \footnotesize
				\begin{itemize}
					\resitem{Web Development - Managing the organization's entire website stack}
					\resitem{Product - Worked on a eCommerce product's UI}
					\resitem{A Rails project for a US based client}
				\end{itemize}
				}
	\end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{{Technical Skills}}
	\begin{description}
		\item[Languages:] { \footnotesize C/C++, Java with good exposure to Python and Ruby
		}
		\item[Stack] { \footnotesize HTML/CSS/JavaScript, RoR, MySQL, OracleDB, PostgreSQL, Docker, Suite of AWS services - Athena, DynamoDB, Redshift, Kinesis, SQS, SNS, EC2, Fargate, ECS, EMR
		}
		\item[Tools/Environment:] {\footnotesize *nix, vim, Git, Bash/zsh
		}

	\end{description} % End Skills list

\newpage

\resheading{\href{https://github.com/dtsdwarak/}{Individual Projects}}

\begin{description}
\item[\href{https://github.com/dtsdwarak/secretshare}{SecretShare}:] { \footnotesize Firefox OS Mobile application to share secrets with Friends. Uses \href{https://onetimesecret.com/}{OneTimeSecret API}, IndexedDB memory store \& HTML/CSS/JavaScript for frontend. Published in Firefox OS Marketplace.}

\item[\href{https://github.com/dtsdwarak/compair}{ComPair}:] { \footnotesize Used to match your Facebook friends/peers and finds the best pair among the given choices. Built with Rails for backend, Bootstrap for UI and Facebook Graph API for user authentication, fetching data and posting/sharing content over Facebook timelines.\color{red}{\bf Won the best creative appliation award at RedHat's OpenShift DevConf 2014, Czech Republic}}

\item[\href{https://dtsdwarak.github.io/lexico/}{Lexico}] { \footnotesize Responsive web application that uses WebSpeech API. Dictionary powered by Wordnik API}

\item[\href{https://github.com/dtsdwarak/fuse}{Fuse}] { \footnotesize Dropbox like file collaboration framework within a LAN to share files. Used Google Plus API for user authentication, WebRTC for realtime video/audio streaming and chat. Designed the WebUI using HTML/CSS/JavaScript, Java servlets for backend and used MySQL for DB.}

\item[\href{https://github.com/dtsdwarak/flames/}{Flames}] { \footnotesize Simple name game built with servlets}

\end{description}

\resheading{{Academic Projects}}

\begin{description}
\item[\href{https://github.com/dtsdwarak/webrtc-demo}{Plugin-free realtime communication via WEBRTC}] { \footnotesize WebRTC based realtime voice and video communication infrastructure with a web frontend}

\item[{Security Analysis of Bitcoin P2P Transactions}] { \footnotesize Analysis of Bitcoin P2P Transactions within the scope of user anonymity.}

\item[{Faster and Secure MD5}] { \footnotesize Modification of MD5 hash algorithm using Wide Pipe and Fast Wide Pipe construction to improve the collision resistance and speed}

\item[{Blind Source Separation using STFT and Spatial Sparsity}] { \footnotesize An approach to solve the Cocktail Party Problem - separate signals of distinct individuals by exploiting their Spatial Sparsity in frequency domain using Short Time Fourier Transform}

\item[{TFIDF Computation using MPI}] {\footnotesize Parallel computation of distributed in-memory graph for text documents across multiple nodes using MPI}

\item[{Building a DB specific kernel}] {\footnotesize Compile a minimal kernel targeted at running only a single instance of database}

\end{description}

\resheading{Certification}
\begin{description}

\item[Cisco Certified Network Associate] { \footnotesize Completed CCNA during October 2011. CSCO ID – CSCO11982736}

\end{description}

\resheading{Extra-curricular Engagements} 

	\begin{description}
		\item[Mozilla Community] {\footnotesize Member of Mozilla India community, served as lead for \href{https://wiki.mozilla.org/NeMo}{Project News Mozilla}, a Mozilla sponsored global project to create regular newspaper articles on digital literacy, open web and data privacy in local languages to create awareness within communities and netizens. \color{red}{\bf Featured in The Hindu, India's leading newspaper - \href{https://www.thehindu.com/sci-tech/technology/Finding-NeMo-with-Mozilla/article12061751.ece}{Finding NeMo with Mozilla}}}
		\item[Editor, \href{http://www.the4cast.com/author/dwarak}{The4Cast Online Tech Magazine}] {\footnotesize Used to review and write articles about gadgets and technology in the past}
		\item[Web Developer/Designer/Part-time Trainer, \href{https://www.networkgeek.in/}{NetworkGeek}] {\footnotesize Developed the site for NetworkGeek training academy. Also a part-time trainer.}
		\item[Volunteer Teacher/Consultant, Teach For India]{\footnotesize Teaching school kids about internet safety, awareness and digital literacy}
		\item[Open Source] {\footnotesize{ Have contributed to projects like ThoughtWorks' Go - Free and  Opensource release automation server, \href{https://mpitutorial.com/about/}{MPITutorial.com} for learning/fun}}
	\end{description}

\end{document}

